Median Maximum Pairwise Distance

### 2020-08-20 main.Rmd
adding text
ways of computing distances added

# A new test statistic

@@

One of the potential ways to evaluate this variation is by computing the pairwise distances between the distributions of the measured variable. We do this through Jensen-Shannon distance which is based on Kullback-Leibler divergence.

The Jensen-Shanon distance between two probability distribution $p_1$ and $p_2$ is given by $$d = [D(p_1, r) + D(p_2, r)]/2 \quad where \quad r = (p_1 + p_2)/2$$ where,
$$D(p_1,p_2) = \int^{\infty}_{-\infty}p_1(x)log\frac{p_1(x)}{p_2(x)}\,dx$$ is the Kullback-Leibler divergence between $p_1$ and $p_2$. Probability distributions are estimated through quantiles instead of kernel density so that there is minimal dependency on selecting kernel or bandwidth.

@@

```{r samenull_2by4}

@@

```{r diffnull_2by4}

@@

```{r diffnull_7by11}
```

@@

```{r diffnull_7by11normal}
```

@@

```{r diffnull_7by11normal2}
```

>>>>

# Computing distance measure

@@

<!-- One of the most important class of divergence is the f-divergence and includes measures like Kullback-Leibler divergence, Hellinger distance etc. The continuous version of f -divergence is given by -->
<!-- $$D_f(P||Q) := \int q(x)f(\frac{p(x)}{q(x)})$$, where -->
<!-- $f : [0,\infty) \rightarrow R \cup \{\infty\}$ is a continuous convex function, and $f(1) = 0$.  -->

The most common divergence measure between distributions is the Kullback-Leibler (KL) divergence introduced by Solomon Kullback and Richard Leibler in 1951. The KL divergence, denoted $D(p(x), q(x))$ is a non-symmetric measure of the difference between two probability distributions $p(x)$ and $q(x)$ and is interpreted as the amount of information lost when $q(x)$ is used to approximate $p(x)$. Although the KL divergence measures the “distance” between two distributions, it is not a distance measure since it is not symmetric. The Jensen-Shannon divergence based on the Kullback-Leibler divergence is symmetric and it always has a finite value. The square root of the Jensen-Shannon divergence is a metric, often referred to as Jensen-Shannon distance. Other common measures of distance are Hellinger distance, total variation distance and Fisher information metric.

In the context of this paper, the pairwise distances between the distributions of the measured variable are computed through Jensen-Shannon distance which is based on Kullback-Leibler divergence and is defined by,

$$JSD(P||Q) = \frac{1}{2}D(P||M) + \frac{1}{2}D(Q||M)$$
where $M = \frac{P+Q}{2}$ and 
$D(P||Q) := \int^\infty_{-\infty} p(x)f(\frac{p(x)}{q(x)})$ is the KL divergence between distributions $p(x)$ and $q(x)$. Probability distributions are estimated through quantiles instead of kernel density so that there is minimal dependency on selecting kernel or bandwidth.

<!-- The Jensen-Shanon distance between two probability distribution $p_1$ and $p_2$ is given by $$d = [D(p_1, r) + D(p_2, r)]/2 \quad where \quad r = (p_1 + p_2)/2$$ where, -->
<!-- $$D(p_1,p_2) = \int^{\infty}_{-\infty}p_1(x)log\frac{p_1(x)}{p_2(x)}\,dx$$ is the Kullback-Leibler divergence between $p_1$ and $p_2$.   -->

@@

```{r samenull_2by4, eval = FALSE}

@@

```{r diffnull_2by4, eval = FALSE}

@@

```{r diffnull_7by11, eval = FALSE}
```

@@

```{r diffnull_7by11normal, eval = FALSE}
```

@@

```{r diffnull_7by11normal2, eval = FALSE}
```
